\Title

### 2022-09-01 Grimaldi-etal-BiolCybernetics.tex
abstract

@@

\newcommand{\AuthorAG}{Antoine Grimaldi}
\newcommand{\AuthorCB}{Camille Besnainou}
\newcommand{\AuthorHL}{Hugo Ladret}
\newcommand{\AuthorLP}{Laurent U Perrinet}

@@

\newcommand{\EmailHL}{hugo.ladret@univ-amu.fr}

@@

\newcommand{\orcidHL}{0000-0001-7999-3751}

@@

\newcommand{\Address}{Institut de Neurosciences de la Timone (UMR 7289); Aix Marseille Univ, CNRS; Marseille, France}%
\newcommand{\Affiliation}{Institut de Neurosciences de la Timone (UMR 7289); Aix Marseille Univ, CNRS;}%
\newcommand{\CityLP}{Marseille, France}%

@@

%%\unnumbered% uncomment this for unnumbered level heads
%\newcommand{\citep}[1]{\cite{#1}}
%\newcommand{\citet}[1]{\cite{#1}}
\newcommand{\seeFig}[1]{see Fig.~\ref{fig:#1}}%{see Figure~\ref{fig:#1}}
%% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
%\usepackage[usenames,dvipsnames]{xcolor} %The package starts from the basic facilities of the color package, and provides easy driver-independent access to several kinds of color tints, shades, tones, and mixes of arbitrary colors.
%\usepackage{tcolorbox} % define boxes that can be customed, has to be loaded after xcolor package
\usepackage{amsmath,amssymb,amsfonts} % amsmath and amssymb packages, useful for mathematical formulas and symbols
%%\usepackage{float} %allows me to use [H] with figures to insert figures in multicol env (poster)
%\usepackage{ulem} %The package provides an \ul (underline) command which will break over line ends; this technique may be used to replace \em (both in that form and as the \emph command), so as to make output look as if it comes from a typewrite. Caution: with this package, bibliography will make unbreakable and underlined journal titles
%\usepackage[switch]{lineno} % add line numbers
%\modulolinenumbers[5]
\usepackage{physics} %The  goal  of  this  package  is  to  make  typesetting  equations  for  physics  simpler,  faster,  and  more  human-readable.
%\usepackage{lineno} %Adds line numbers to selected paragraphs with reference possible through the LaTeX \ref and \pageref cross reference mechanism.
%\usepackage{hyperref} %The hyperref package is used to handle cross-referencing commands in LaTeX to produce hypertext links in the document
%\hypersetup{
%    colorlinks = false,
%    hidelinks
%    %linkbordercolor = {white},
%}
%\usepackage{array} %An extended implementation of the array and tabular environments which extends the options for column formats, and provides “programmable” format specifications.
%\usepackage{multicol} %Multicol defines a multicols environment which typesets text in multiple columns
%%\usepackage{wrapfig} %Allows figures or tables to have text wrapped around them. wrapfig is used when calling multicols
% \usepackage[position=top]{subfig} %The package provides support for the manipulation and reference of small or ‘sub’ figures and tables within a single figure or table environment. Linked to subfloat.
% for units
\usepackage{siunitx}%The siunitx package provides a  set  of  tools  for  authors  to  typeset  quantities  in  aconsistent  way.

@@

\author*[1]{\fnm{Antoine} \sur{Grimaldi}}\email{antoine.grimaldi@univ-amu.fr}

\author[2]{\fnm{Amélie} \sur{Gruel}}\email{amelie.gruel@univ-cotedazur.fr}

\author[2]{\fnm{Jean} \sur{Martinet}}\email{jean.martinet@univ-cotedazur.fr}

\author[1]{\fnm{Laurent} \sur{Perrinet}}\email{laurent.perrinet@univ-amu.fr}

\affil[1]{\orgdiv{Department}, \orgname{\Affiliation}, \orgaddress{\street{Street}, \city{Marseille}, \postcode{13005}, \country{France}}}
\affil[2]{\orgdiv{SPARKS}, \orgname{Université Côte d'Azur, CNRS, I3S}, \orgaddress{\street{2000 Rte des Lucioles}, \city{Sophia-Antipolis}, \postcode{06900}, \country{France}}}

%
%\ninept
%
%
%\abstract{
%Abstract
%}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{abeles1982role}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.

>>>>

%Call for papers: Biological Cybernetics Special Issue: What can Computer Vision learn from Visual Neuroscience?
%Computer vision still struggles to solve many problems as quickly and accurately as our brain does, despite its tremendous progress using deep learning over the last decade. Current challenges include geometry understanding, dynamic scene understanding, few shot learning of novel objects, anomaly and counterfeit detection, stable reproduction of imaginary visuals, and more. The brain achieves all these on a low computational cost and power budget (i.e., tens of watts), whereas the state-of-the-art computer vision models require multiple graphics processors consuming kilowatts of power. Hence, new inspirations from the brain could make computer vision more efficient, robust, and capable of continuous learning and adaptation. Although visual neuroscience literature provides knowledge about neuronal selectivities and early processing of visual inputs, computational modelling of neuronal and network behaviours with some degree of biological constraints and characteristics is an important tool to address many of the challenges facing computer vision. With new neuroscientific insights about deep cortical vision processing using the latest stimulation and recording technologies, it is important that we strive to understand the underlying computations and learning mechanisms, so that artificial vision systems with similar efficiency can be developed. This special issue invites original research and review articles related to topics in biological vision that can potentially benefit computer vision systems. The following is a non-exhaustive list of topics in biological vision that can also benefit computer vision systems.
%● Active vision’s role in visual search, scene understanding, social interactions, etc.
%● Learning in the visual system. Learning in biology is continual, few-shot, and adversarially robust.
%● The roles of recurrent and top-down connections in the visual cortex.
%● Spike based spatiotemporal processing and its implications for neuromorphic vision.
%● Motion perception in dynamic environments.
%● Neural coding schemes in the visual system (e.g., sparse coding, predictive coding, and temporal coding.)
%● The roles of attention mechanisms in biological vision.

@@

\newcommand{\FirstAG}{Antoine}
\newcommand{\LastAG}{Grimaldi}
\newcommand{\AuthorAG}{\FirstAG \LastAG}
\newcommand{\FirstLP}{Laurent U}
\newcommand{\LastLP}{Perrinet}
\newcommand{\AuthorLP}{\FirstLP \LastLP}

@@

@@

@@

\newcommand{\Department}{Institut de Neurosciences de la Timone (UMR 7289)}%
\newcommand{\Affiliation}{Aix Marseille Univ, CNRS}%
\newcommand{\Street}{27 boulevard Jean Moulin}%
\newcommand{\City}{Marseille}%
\newcommand{\Country}{France}%

@@

%%\unnumbered% uncomment this for unnumbered level heads
\newcommand{\citep}[1]{\cite{#1}}
\newcommand{\citet}[1]{\cite{#1}}
\newcommand{\seeFig}[1]{see Fig.~\ref{fig:#1}}%{see Figure~\ref{fig:#1}}
%% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
%\usepackage[usenames,dvipsnames]{xcolor} %The package starts from the basic facilities of the color package, and provides easy driver-independent access to several kinds of color tints, shades, tones, and mixes of arbitrary colors.
%\usepackage{tcolorbox} % define boxes that can be customed, has to be loaded after xcolor package
\usepackage{amsmath,amssymb,amsfonts} % amsmath and amssymb packages, useful for mathematical formulas and symbols
%%\usepackage{float} %allows me to use [H] with figures to insert figures in multicol env (poster)
%\usepackage{ulem} %The package provides an \ul (underline) command which will break over line ends; this technique may be used to replace \em (both in that form and as the \emph command), so as to make output look as if it comes from a typewrite. Caution: with this package, bibliography will make unbreakable and underlined journal titles
%\usepackage[switch]{lineno} % add line numbers
%\modulolinenumbers[5]
\usepackage{physics} %The  goal  of  this  package  is  to  make  typesetting  equations  for  physics  simpler,  faster,  and  more  human-readable.
%\usepackage{lineno} %Adds line numbers to selected paragraphs with reference possible through the LaTeX \ref and \pageref cross reference mechanism.
%\usepackage{hyperref} %The hyperref package is used to handle cross-referencing commands in LaTeX to produce hypertext links in the document
%\hypersetup{
%    colorlinks = false,
%    hidelinks
%    %linkbordercolor = {white},
%}
%\usepackage{array} %An extended implementation of the array and tabular environments which extends the options for column formats, and provides “programmable” format specifications.
%\usepackage{multicol} %Multicol defines a multicols environment which typesets text in multiple columns
%%\usepackage{wrapfig} %Allows figures or tables to have text wrapped around them. wrapfig is used when calling multicols
% \usepackage[position=top]{subfig} %The package provides support for the manipulation and reference of small or ‘sub’ figures and tables within a single figure or table environment. Linked to subfloat.
% for units
\usepackage{siunitx}%The siunitx package provides a  set  of  tools  for  authors  to  typeset  quantities  in  aconsistent  way.

@@

\author*{\fnm{Antoine} \sur{Grimaldi}}\email{antoine.grimaldi@univ-amu.fr}

\author{\fnm{Laurent} \sur{Perrinet}}\email{laurent.perrinet@univ-amu.fr}

\affil{\orgdiv{\Department}, \orgname{\Affiliation}\\ \orgaddress{\street{\Street}, \city{\City}, \postcode{13005}, \country{\Country}}}

%\author*[1]{\fnm{Antoine} \sur{Grimaldi}}\email{antoine.grimaldi@univ-amu.fr}
%
%\author[2]{\fnm{Amélie} \sur{Gruel}}\email{amelie.gruel@univ-cotedazur.fr}
%
%\author[2]{\fnm{Jean} \sur{Martinet}}\email{jean.martinet@univ-cotedazur.fr}
%
%\author[1]{\fnm{Laurent} \sur{Perrinet}}\email{laurent.perrinet@univ-amu.fr}
%
%\affil[1]{\orgdiv{Department}, \orgname{\Affiliation}, \orgaddress{\street{Street}, \city{Marseille}, \postcode{13005}, \country{France}}}
%\affil[2]{\orgdiv{SPARKS}, \orgname{Université Côte d'Azur, CNRS, I3S}, \orgaddress{\street{2000 Rte des Lucioles}, \city{Sophia-Antipolis}, \postcode{06900}, \country{France}}}

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

\abstract{
\Abstract
}

%
%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{abeles1982role}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.
